\documentclass[10pt,a4paper]{article}

% Packages
\usepackage[margin=0.36in, top=0.25in, bottom=0.25in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{xcolor}
\usepackage{parskip}
\usepackage{microtype}

% Colors
\definecolor{primary}{RGB}{99, 91, 255}
\definecolor{darktext}{RGB}{50, 50, 50}

% Formatting
\pagestyle{empty}
\setlength{\parindent}{0pt}
\hypersetup{colorlinks=true, linkcolor=primary, urlcolor=primary}
\emergencystretch=2em

% Section formatting
\titleformat{\section}
{\color{primary}\fontsize{10.8}{13}\selectfont\bfseries\uppercase}
{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{7pt}{4pt}

% Custom commands
\newcommand{\resumeItem}[1]{\item[\textcolor{primary}{\textbullet}] #1}
\newcommand{\skillCategory}[2]{\textbf{#1:} #2}

\begin{document}

% Header
\begin{center}
    {\LARGE\bfseries Bhaskar Lamba}\\[4pt]
    \small
    \faPhone\ +91 9306505417 \quad
    \faEnvelope\ \href{mailto:bhaskarlamba@gmail.com}{bhaskarlamba@gmail.com} \quad
    \faLinkedin\ \href{https://www.linkedin.com/in/bhaskar-lamba-5268391b2/}{linkedin.com/in/bhaskar-lamba-5268391b2}
\end{center}
\vspace{6pt}

% Education
\section{Education}
\small
\textbf{IIT Kanpur} \hfill \raisebox{-0.5\baselineskip}{GPA 8.1/10}\\
Bachelor of Technology, Mechanical Engineering

% Work Experience
\section{Work Experience}
\small

\textbf{Senior Software Applications Engineer} \hfill Aug'24 -- Present\\
\textit{Oracle India Pvt. Ltd.}
\begin{itemize}[leftmargin=1.05em, nosep, topsep=0pt, itemsep=0pt, parsep=0pt]
    \resumeItem{Drive full-stack ownership of two enterprise talent management products --- \textbf{Succession Management} and \textbf{Talent Review} --- serving \textbf{400+ business customers}, covering UI, backend, and production reliability.}
    \resumeItem{Independently scoped and delivered \textbf{30+ product features} end-to-end, consistently meeting tight delivery timelines as short as \textbf{3--4 days}.}
    \resumeItem{Designed and shipped a \textbf{customer-facing AI agent} for the \textbf{Succession Management} product, enabling users to perform core workflows --- succession plan creation, team succession status queries, and criticality analysis --- through natural language, reducing manual navigation overhead.}
    \resumeItem{Serve as a go-to engineer for production incident resolution, code reviews, and knowledge transfers within a \textbf{5-member} team, maintaining high product availability and team alignment.}
\end{itemize}

\vspace{1pt}
\textbf{Applications Engineer} \hfill Jun'22 -- Aug'24\\
\textit{Oracle India Pvt. Ltd.}
\begin{itemize}[leftmargin=1.05em, nosep, topsep=0pt, itemsep=0pt, parsep=0pt]
    \resumeItem{Contributed to feature development across \textbf{Succession Management} and \textbf{Talent Review} enterprise products, building UI components and \textbf{REST APIs} as part of a cross-functional team.}
    \resumeItem{Orchestrated the migration of \textbf{\textasciitilde90\%} of the product from a legacy Java-based system to a modern web architecture, reducing page load times by \textbf{70\%} and modernizing the platform for enterprise customers.}
\end{itemize}

\vspace{1pt}
\textbf{Project Intern} \hfill Jun'21 -- Jul'21\\
\textit{Oracle India Pvt. Ltd.}
\begin{itemize}[leftmargin=1.05em, nosep, topsep=0pt, itemsep=0pt, parsep=0pt]
    \resumeItem{Designed and implemented conversation flows within a chatbot to enhance user experience through intuitive interactions across multiple functionalities.}
    \resumeItem{Utilized \textbf{REST APIs} to retrieve and display data within the chat interface, providing users with timely and relevant information.}
    \resumeItem{Managed chatbot development from inception to completion, including comprehensive documentation, within a challenging \textbf{four-week timeline}.}
    \resumeItem{Recognized for outstanding performance with a \textbf{Pre-Placement Offer from Oracle}.}
\end{itemize}

% Projects
\section{Projects}
\small

\textbf{Online Fitness Rehab Coaching Platform} \hfill \href{https://workout-planner-app-e7087.firebaseapp.com/}{\faLink}\\
\textit{Firebase, Codex}
\begin{itemize}[leftmargin=1.05em, nosep, topsep=0pt, itemsep=0pt, parsep=0pt]
    \resumeItem{Built and deployed a \textbf{Firebase web app} to streamline \textbf{online fitness rehab} and coaching workflows, enabling coaches to send \textbf{structured workouts} and collect client feedback.}
    \resumeItem{Collaborated with \textbf{Codex} to rapidly iterate on product features and launched the app live on \textbf{Firebase within a single day}.}
    \resumeItem{Use the platform personally and with other coaches to manage \textbf{client workout delivery}, \textbf{feedback loops}, and rehab/coaching operations.}
\end{itemize}

\vspace{1pt}
\textbf{My Cricket Heroes} \hfill \textit{Web Application}\\
\textit{Apr'23 -- Jun'23}
\begin{itemize}[leftmargin=1.05em, nosep, topsep=0pt, itemsep=0pt, parsep=0pt]
    \resumeItem{Collaborated in a team of five to conceptualize and develop the \textbf{MyHeroes} application, mirroring platforms like \textbf{Dream11} to improve sports engagement.}
    \resumeItem{Tested the application concept during the \textbf{IPL'23 season}, integrating live scores and player statistics for \textbf{real-time updates}.}
    \resumeItem{Steered the design, coding, and launch of the initial version within a \textbf{two-week} timeframe.}
    \resumeItem{Achieved a \textbf{75\% increase} in user engagement during IPL'23 through live score and player information integration.}
    \resumeItem{Developed a \textbf{fully automated scoring system} for real-time match updates.}
\end{itemize}

% Skills
\section{Technical Skills}
\small
\skillCategory{Programming Languages}{C, C++, Java, JavaScript, Python, Dart}\\[1pt]
\skillCategory{Web \& Mobile}{HTML, CSS, React, React Native, Next.js}\\[1pt]
\skillCategory{Backend \& Databases}{REST APIs, CRUD APIs, Node.js, Spring Boot, MySQL, Firebase}\\[1pt]
\skillCategory{Tools}{Oracle VBS, Android Studio, Git, Postman, Codex}

% Achievements
\section{Achievements}
\small
\begin{itemize}[leftmargin=1.05em, nosep, topsep=0pt, itemsep=0pt, parsep=0pt]
    \resumeItem{Secured \textbf{AIR-1558} in JEE (Advanced) 2018 among approx. 2 lakh candidates.}
\resumeItem{Won IIT Kanpur's \textbf{Outstanding Freshman Award} for exceptional performance, given to only \textbf{2 students} from the batch.}
    \resumeItem{Awarded \textbf{Institute Silver Medal} for achieving a Gold Medal and breaking the meet record in the Inter-IIT Sports Meet.}
    \resumeItem{Received \textbf{Sports Scholarship} from the Games and Sports Council, IIT Kanpur for two consecutive years.}
\end{itemize}

\end{document}
